### 2025-05-07 chapters/conclusion.tex
Extended conclusion

>>>>

We've gained a precise, analytic understanding of some simple concepts in the phenomenological study of \gls{qcd} -- hopefully, at a level of detail that can accelerate your learning.
%
While it is \textit{always} helpful to have a solid understanding of the basics, the accuracy and utility of the results we discuss in this thesis can be improved by more detailed technical studies.
%
Precision calculations of \PIRANHA-groomed jet substructure, our new parametrization of energy correlators, and general \glspl{ewoc}, will enable more detailed comparisons of experimental and theoretical results, and lead to a deeper analytic understanding of the substructure observables we developed.
%
Additionally, the comparison of experiment and theory will need to be accompanied by more detailed modelling of uncertainties, such as the techniques of unfolding and re-weighting discussed in \App{pollution-models}.

More detailed studies of the mass \gls{ewoc}, for example, may lead to complementary measurements of masses of the particles of the standard model which decay hadronically.
%
The most precise existing measurements of the \(W\) boson mass involve leptonic decays of the \(W\) boson, rather than hadronic decays, and require a detailed understanding of recoil and missing energy;
%
the use of the mass \gls{ewoc} allows us to study the mass of the \(W\) boson with hadronic decays and without sensitivity to recoil%
\footnote{
    I thank Christoph Paus for pointing out this feature.
}
%
The study of the three-point mass \gls{ewoc} may also lead to a more precise measurement of the mass of the top quark, whose value sensitively determines the long-term fate of the standard model vacuum \cite{Alekhin:2012py}.

Furthermore, the substructure observables discussed in this thesis may be refined and honed for specific phenomenological tasks with more detailed optimization.
%
For example, we have already presented in \App{pufrenzy} a simple optimization of the \gls{rsf} \PIRANHA{} grooming procedure for the removal of pileup;
%
however, optimization of more general \glslink{rs}{recursive subtraction} algorithms using machine learning and more detailed recursive algorithms may lead to more robust \PIRANHA{} grooming techniques which are nonetheless tree-based, efficient, and connected to event-space geometry.
%
Optimization of the weights of \glslink{penc}{projected} and \glslink{renc}{resolved} energy correlators may allow us to perform interesting studies which classify the behavior of dense, high-multiplicity nuclear environments such as the quark-gluon plasma;
%
the efficient, tunable behavior of PENCs and RENCs may be used to test different models of QGP formation and scattering within the QGP.
%
Similarly, optimization of the weights of more general \glspl{ewoc} may enable even deeper understanding of the behavior of our microscopic universe which is more robust to the presence of additive contamination.
%
For example, we saw in the low-multiplicity environment of proton-proton collisions that mass \glspl{ewoc} which utilize higher energy weights lead to more robust mass extraction (see \Tab{energyweights} of \Sec{ewoc-mass}).
%
The high-multiplicity environment of heavy ion has an even more formidable underlying event of contaminating radiation whose effects can also be mitigated by the use of \glspl{ewoc} with higher energy weights.
%
Even further, the use of observables other than mass%
\footnote{
    For example, we mentioned in \Sec{ewoc-intro} that \glspl{ewoc} based on pairwise \textit{formation times} \(\tau_{ij} = \max{\le(E_i, E_j\ri)} / m^2_{ij}\) probe the time scales associated with the production of high energy structures within jets, and may be useful in probing the evolution of jets in heavy ion collisions.
}
%
may lead to additional power in classifying the behavior of the QGP and testing models of heavy ion collisions.
%
Optimizing the behavior of \glspl{ewoc} over both energy weights \textit{and} a wide space of pairwise observables (or even \(N\)-point observables) may lead to \glspl{ewoc} which discriminate sharply between different models of the QGP, and of particle production in high-energy scattering events in general.
